---
title: "writing functions"
author: "Longyi Zhao"
date: "2023-10-26"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6, 
  out.width = "90%"
)

theme_set (theme_minimal() +theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis", 
  ggplots.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_disrete = scale_fill_viridis_d
```

output on this page is fixed 
```{r}
set.seed(1)
```

```{r}
x_vec = rnorm(20, mean = 5, sd =0.3)
```

```{r}
(x_vec - mean(x_vec))/sd(x_vec)
```

x is the input
everytime when it see x, put into the function 
```{r}
z_score = function(x) {
  z = (x-mean(x))/sd(x)
  if (!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at least 2 numbers to get z score")
  }
  z # return z
}
```

check that this works
```{r}
z_score(x = x_vec)
```

```{r, error = TRUE}
z_score(x=3) # single number no sd 

z_score(x = c("my", "name")) # character variable no mean and sd 

z_score(x = c(TRUE, FALSE, TRUE, TRUE))
```

## Multiple output

write a function that returns the mean and sd from a sample of numbers
find a way to return multiple things at the same time, for example both mean and sd, for example return a dataframe using tibble 
```{r}
mean_and_sd = function(x) {
   z = (x-mean(x))/sd(x)
  if (!is.numeric(x)) {
    stop("Argument should be numbers")
  } else if (length(x) < 2) {
    stop("You need at least 2 numbers to get z score")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x, 
    sd = sd_x
  )
  
}
```

check 
```{r}
mean_and_sd(x_vec)
```


## Multiple Inputs: start getting means and sds

```{r}
x_vec = rnorm(n = 30, mean = 5, sd = 0.5)

tibble(
  mean = mean(x_vec), 
  sd = sd(x_vec)
)

```

lets write a function that uses `n`, a true mean and true sd as inputs
mu = mean 
sigma = sd
```{r}
sim_mean_sd = function(n_obs, mu, sigma) {
  
  x_vec = rnorm(n = n_obs, mean = mu, sd = sigma)

  tibble(
    mean = mean(x_vec), 
    sd = sd(x_vec)
  )

}

sim_mean_sd(n_obs = 30, mu = 5, sigma = 0.5)
# get different mean and sd each time run the function 

sim_mean_sd (12, 12, 4) # positional matching
sim_mean_sd (mu = 12, n_obs = 12, sigma = 4) # can name in different order 
```

## Loading LoTR data

```{r}
fellowship_ring = readxl::read_excel("./data/LotR_Words.xlsx", range = "B3:D6") |>
  mutate(movie = "fellowship_ring")

lotr_load_and_tidy = function(path = "data/LotR_Words.xlsx", cell_range, movie_name) {
  movie_df = readxl::read_excel(path, range = cell_range) |>
  mutate(movie = movie_name) |>
  janitor::clean_names() |>
    pivot_longer(
      female:male, 
      names_to = "sex", 
      values_to = "words"
    ) |>
    select(movie, everything())
  
  movie_df
}

lotr_load_and_tidy(cell_range =  "B3:D6", movie_name = "fellowship_ring")
lotr_load_and_tidy(cell_range =  "F3:H6", movie_name = "two_towers")
lotr_load_and_tidy(cell_range =  "J3:L6", movie_name = "return_king")
```














